Weighted Visibly Pushdown Automata and Automated Music Transcription

### 2021-04-29 main.tex
revise definition label theory

\title{Weighted Visibly Pushdown Automata and Automated Music Transcription}
%\author{Florent Jacquemard}
%\institute{INRIA \& CNAM, Paris, France\\
%\email{florent.jacquemard@inria.fr}}

@@

\begin{document}
\thispagestyle{empty}
\maketitle
\abstract{\ldots}

Symbolic Weighted (SW) extension of symbolic automata where...

\paragraph{Semirings.}
We shall consider semiring domains for weight values.
%
A \emph{semiring} $\< \Semiring, \oplus, \zero, \otimes, \one>$ 
is a structure with a domain~$\Semiring$,
equipped with two associative
binary operators~$\oplus$ and $\otimes$
with respective neutral elements $\zero$ and $\one$ and such that:
%$\< \mathbb{S}, \oplus, \zero>$ is a commutative monoid
%$\< \mathbb{S}, \otimes, \one>$ is a monoid
$\oplus$ is commutative, 
$\otimes$ distributes over~$\oplus$:  $\forall x, y, z \in \mathbb{S}$,
$x \otimes (y \oplus z) = (x \otimes y) \oplus (x \otimes z)$, 
%  and $(x \oplus y) \otimes z = (x \otimes z) \oplus (y \otimes z)$;
and $\zero$ is absorbing for~$\otimes$: 
$\forall x\in \mathbb{S}$, $\zero \otimes x = x \otimes \zero = \zero$.
%Components of a semiring~$\Semiring$ may be subscripted by~$\Semiring$ when needed.
%We simply write $x \in \Semiring$ to mean $x \in \mathbb{S}$.
%
In the application presented in this paper, intuitively,
$\oplus$ selects an optimal value amongst two values and 
$\otimes$ combines two values into a single value.

and let $\< \Semiring, \oplus, \zero, \otimes, \one>$ be a {semiring},

%\noindent
A semiring $\Semiring$ 
is \emph{monotonic} \wrt a partial ordering~$\leq$ 
iff for all $x, y, z  \in \Semiring$,  $x \leq y$ implies
$x \oplus z \leq y \oplus z$,
$x \otimes z \leq y \otimes z$
and $z \otimes x \leq z \otimes y$,
%
and it is \emph{superior} %\wrt a partial ordering~$\leq$
\wrt~$\leq$ iff for all $x, y \in \Semiring$,  
$x \leq x \otimes y$ and 
$y \leq x \otimes y$~\cite{Huang08advanceddynamic}.
The latter property corresponds to the 
\emph{non-negative weights} condition in shortest-path algorithms~\cite{Dijkstra59anote}.
Intuitively, it means that combining elements always increase their weight. 
% always get worse in term of weight
Note that when $\Semiring$ is superior \wrt~$\leq$, then $\one \leq \zero$
and moreover, for all $x \in \Semiring$, $\one \leq x \leq \zero$.

Every idempotent semiring~$\Semiring$ induces 
a partial ordering~$\leq_\Semiring$ 
called the \emph{natural ordering} of~$\Semiring$
and defined by: 
%implicitly defined by the semiring $\Semiring$ 
for all $x$ and $y$,
$x \leq_\Semiring y \;\mbox{iff}\; x \oplus y = x$.
This ordering is sometimes defined in the opposite direction~\cite{DrosteKuich09semirings};
The above definition follows \cite{Mohri02semiring}, 
and coincides than the usual ordering on the Tropical semiring (\emph{min-plus}).
%
It holds that $\Semiring$ is {monotonic} \wrt~$\leq_\Semiring$.
An idempotent Semiring $\Semiring$~is called \emph{total} if
it~$\leq_\Semiring$ is total
\ie when for all $x, y \in \Semiring$, either $x \oplus y = x$ or $x \oplus y = y$.

We shall consider below infinite sums with~$\oplus$.
A semiring~$\Semiring$ is called \emph{complete} 
if for every family
$(x_i)_{i \in I}$ %$\{ x_i \mid i \in I \}$
of elements of $\dom(\Semiring)$ over an index set $I \subset \mathbb{N}$,
the infinite sum $\bigoplus_{i \in I} x_i$
is well-defined and in $\dom(\Semiring)$,
and the following properties hold:
\begin{description}
\item[$i.$]
\emph{infinite sums extend finite sums:}
$\displaystyle\bigoplus_{i \in \emptyset} x_i = \zero$,\quad 
      $\forall j\in \mathbb{N}, \displaystyle\bigoplus_{i \in \{ j \}} x_i = x_j$,\quad
      $\forall j, k\in \mathbb{N}, j\neq k, 
      \displaystyle\bigoplus_{i \in \{ j, k \}} x_i = x_j \oplus x_k$,
%
\item[$ii.$]
\emph{associativity and commutativity:}
for all $I \subseteq \mathbb{N}$
and all partition $(I_{j})_{j \in J}$ of $I$, %\subseteq \mathbb{N}$, 
\(
\displaystyle
\bigoplus_{j \in J}\bigoplus_{i \in I_j} x_i = 
\bigoplus_{i \in I} x_i
\),
%
\item[$iii.$] 
\emph{distributivity of product over infinite sum:}\\
for all $I \subseteq \mathbb{N}$,
\(
\displaystyle
\bigoplus_{i \in I} (x \otimes y_i) = x \otimes \bigoplus_{i\in I} y_i\), and
\(
\displaystyle
\bigoplus_{i \in I} (x_i \otimes y) = (\bigoplus_{i \in I} x_i ) \otimes y\).
\end{description}

\section{SW Automata and Transducers}
\label{section:transducer}
We follow the approach of~\cite{Mohri03EDWA} for the computation of distances
between words with transducers.

The following definition of weighted transducers over infinite alphabets 
generalizes weighted transducers over finite alphabets, see  e.g.~\cite{Mohri03EDWA}, 
by considering weight functions generalizing the guards of symbolic automata

Let $\Sigma$ and $\Delta$ be respectively an input and output \emph{alphabets}, 
which are finite or infinite sets of symbols, and let $\Semiring$ be a semiring.
%
A \emph{label theory} 
is a 4-uplet of recursively enumerable sets:
%$\Phi_0$, \Phi_\Sigma \uplus \Phi_\Delta \uplus \Phi_{\Sigma, \Delta}$ 
$\Phi_0$ containing constant functions valued in $\Semiring$, 
$\Phi_\Sigma$ and $\Phi_\Delta$, 
containing unary functions in $\Sigma \to \Semiring$, resp. $\Delta \to \Semiring$, 
and $\Phi_{\Sigma, \Delta}$  containing binary functions in $\Sigma \times \Delta \to \Semiring$.
Moreover, we assume that each of these sets is closed under $\oplus$ and $\otimes$, 
and all partial applications of functions $\Phi_{\Sigma, \Delta}$, 
resp. 
$f_a: y \mapsto f(a, y)$ for $a \in \Sigma$ and $y \in \Delta$
and 
$f_b: x \mapsto f(x, b)$ for $b \in \Delta$ and $x \in \Sigma$, 
belong resp. to $\Phi_\Sigma$ and $\Phi_\Delta$.

@@

Let $\Sigma$ be an input alphabet, finite (large) or infinite,
that we assume partitioned into :
\begin{itemize}
\item a set $\Sigmai$ of \emph{internal symbols} denoted $a$,
\item a set $\Sigmac$ of \emph{call symbols} denoted $\call{a}$,
\item a set $\Sigmar$ of \emph{return symbols} denoted $\return{a}$.
\end{itemize}
In order to simplify notations, and following the definition of Section~\ref{section:transducer}, 
we shall write respectively~$\Phii$, $\Phic$, $\Phir$ and~$\Phicr$
for~$\Phi_\Sigmai$, $\Phi_\Sigmac$, $\Phi_\Sigmar$ and~$\Phi_{\Sigmac, \Sigmar}$,

\begin{definition}
A \emph{Symbolic Weighted Visibly Pushdown Automata} (\SWVPA) $A$ 
over the input $\Sigma = \Sigmai \uplus \Sigmac \uplus \Sigmar$
and the semiring $\Semiring$ is a tuple
$T = \< Q, P, \init, \weii, \weic, \weir, \weie, \final >$,
where $Q$ is a finite set of states, 
$P$ is a finite set of stack symbols, 
$\mathsf{in} : Q \to \Semiring$, 
respectively $\mathsf{out} : Q \to \Semiring,$
are functions defining the weight for entering, 
respectively leaving, a state, 
and 
$\weii : Q \times Q \to \Phii$,  
$\weic : Q \times Q \times P \to \Phic$,  
$\weir : Q \times P \times Q \to \Phicr$,  
$\weie : Q \times Q \to \Phir$,  
are transition functions.
\end{definition}
%
Similarly as in Section~\ref{section:transducer}, 
we extend the above transition functions as follows
for all $q, q' \in Q$, $p \in P$, 
$a \in \Sigmai$, 
$\call{c} \in \Sigmac$, 
$\return{r} \in \Sigmar$, 
overloading the names for simplicity:
\[
\begin{array}{lll}
\weii: Q \times \Sigmai \times Q \to \Semiring & 
\weii(q, a, q') = \phi_\mathsf{i}(a) & 
\mathrm{where~} \phi_\mathsf{i} = \weii(q, q')\\
%
\weic: Q \times \Sigmac \times Q \times P \to \Semiring & 
\weic(q, \call{c}, q', p) = \phi_\mathsf{c}(\call{c}) & 
\mathrm{where~} \phi_\mathsf{c} = \weic(q, q', p)\\
%
\weir: Q \times \Sigmac \times P \times \Sigmar \times Q \to \Semiring & 
\weir(q, {\call{c}},  p, {\return{r}}, q') = \phi_\mathsf{r}({\call{c}},  {\return{r}}) & 
\mathrm{where~} \phi_\mathsf{r} = \weir(q, p, q')\\
%
\weie: Q \times \Sigmar \times Q \to \Semiring & 
\weie(q, {\return{r}}, q') = \phi_\mathsf{e}({\return{r}}) &
\mathrm{where~} \phi_\mathsf{e} = \weie(q, q')\\
\end{array}      
\]

\noindent
The intuition is the following for the above transitions.
\begin{description}
\item $\weii$ : read the input internal symbol $a$, change state to $q'$.
\item $\weic$ : read the input symbol $\call{c}$, push it to the stack along with $p$, change state to $q'$.
\item $\weir$ : when the stack is not empty, 
      read and pop from stack a pair made of $\call{c}$ and $p$, 
      read the input symbol $\return{r}$, change state to $q'$.
      In this case, the weight function $\phi_\mathsf{r}$ checks a matching between the call and return symbols.
\item $\weie$ : when the stack is empty, 
      read the input symbol $\call{r}$, change state to $q'$.
\end{description}

@@

\noindent
The weight associated by $A$ to $s \in \Sigma^*$
is then defined as follows by empty stack computation: 
\[
A(s)  = 
{\displaystyle\bigoplus_{q, q' \in Q}} \textstyle
\mathsf{in}(q) \mathop{\otimes} 
\weight_A\bigl(\config{q}{\bot}, s, \config{q'}{\bot}\bigr) 
\mathop{\otimes} \mathsf{out}(q').
\]

@@

>>>>

\title{Weighted Visibly Pushdown Automata and Automated Music Transcription}
\author{Florent Jacquemard}
%\institute{INRIA \& CNAM, Paris, France\\
%\email{florent.jacquemard@inria.fr}}

@@

\begin{document}
\thispagestyle{empty}
\maketitle

%\begin{abstract}
%Symbolic Weighted (SW) extension of symbolic automata...
%\end{abstract}

\section{SW Automata and Transducers}
\label{section:transducer}

We follow the approach of~\cite{Mohri03EDWA} for the computation of distances
between words with weighted transducers, and propose models of weighted automata 
and weighted transducers over infinite alphabets.

These models generalize weighted automata and transducers over finite alphabets, see  e.g.~\cite{Mohri03EDWA}, 
by labeling each transition with a weight functions that takes the 
input and output symbols as parameters, instead of a simple weight value.
These functions are similar to the guards of symbolic automata~\cite{Veanes13ciaa}, 
but they can return values in an arbitrary semiring, 
where the latter guards are restricted to the Boolean semiring.

\subsection{Semirings}
\label{section:semiring}
We shall consider semiring domains for weight values.
%
A \emph{semiring} $\< \Semiring, \oplus, \zero, \otimes, \one>$ 
is a structure with a domain~$\Semiring$,
equipped with two associative
binary operators~$\oplus$ and $\otimes$
with respective neutral elements $\zero$ and $\one$ and such that:
%$\< \mathbb{S}, \oplus, \zero>$ is a commutative monoid
%$\< \mathbb{S}, \otimes, \one>$ is a monoid
$\oplus$ is commutative, 
$\otimes$ distributes over~$\oplus$:  $\forall x, y, z \in \mathbb{S}$,
$x \otimes (y \oplus z) = (x \otimes y) \oplus (x \otimes z)$, 
%  and $(x \oplus y) \otimes z = (x \otimes z) \oplus (y \otimes z)$;
and $\zero$ is absorbing for~$\otimes$: 
$\forall x\in \mathbb{S}$, $\zero \otimes x = x \otimes \zero = \zero$.
%Components of a semiring~$\Semiring$ may be subscripted by~$\Semiring$ when needed.
%We simply write $x \in \Semiring$ to mean $x \in \mathbb{S}$.
%
% In the application presented in this paper, intuitively,
% $\oplus$ selects an optimal value amongst two values and 
% $\otimes$ combines two values into a single value.
%and let $\< \Semiring, \oplus, \zero, \otimes, \one>$ be a {semiring},

\noindent
A semiring $\Semiring$ is \emph{commutative} if $\otimes$ is commutative.
It is \emph{idempotent} if for each $x \in \dom(\Semiring)$, $x \oplus x = x$.
%
Following the terminology of~\cite{Mohri02semiring},
when $\forall x \in \dom(\Semiring), \one \oplus x = \one$,
the semiring $\Semiring$ is is called \emph{bounded}.
Note that every bounded semiring is idempotent:
by boundedness, 
$\one \oplus \one = \one$, and idempotency follows by multiplying
both sides by $x$ and distributing.

% \noindent
A semiring $\Semiring$ 
is \emph{monotonic} \wrt a partial ordering~$\leq$ 
iff for all $x, y, z  \in \Semiring$,  $x \leq y$ implies
$x \oplus z \leq y \oplus z$,
$x \otimes z \leq y \otimes z$
and $z \otimes x \leq z \otimes y$,
%
and it is \emph{superior} %\wrt a partial ordering~$\leq$
\wrt~$\leq$ iff for all $x, y \in \Semiring$,  
$x \leq x \otimes y$ and 
$y \leq x \otimes y$~\cite{Huang08advanceddynamic}.
The latter property corresponds to the 
\emph{non-negative weights} condition in shortest-path algorithms~\cite{Dijkstra59anote}.
Intuitively, it means that combining elements always increase their weight. 
% always get worse in term of weight
Note that when $\Semiring$ is superior \wrt~$\leq$, then $\one \leq \zero$
and moreover, for all $x \in \Semiring$, $\one \leq x \leq \zero$.

Every idempotent semiring~$\Semiring$ induces 
a partial ordering~$\leq_\Semiring$ 
called the \emph{natural ordering} of~$\Semiring$
and defined by: 
%implicitly defined by the semiring $\Semiring$ 
for all $x$ and $y$,
$x \leq_\Semiring y \;\mbox{iff}\; x \oplus y = x$.
This ordering is sometimes defined in the opposite direction~\cite{DrosteKuich09semirings};
The above definition follows \cite{Mohri02semiring}, 
and coincides than the usual ordering on the Tropical semiring (\emph{min-plus}).
%
It holds that $\Semiring$ is {monotonic} \wrt~$\leq_\Semiring$.
An idempotent semiring $\Semiring$~is called \emph{total} if
it~$\leq_\Semiring$ is total
\ie when for all $x, y \in \Semiring$, either $x \oplus y = x$ or $x \oplus y = y$.

\medskip
We shall consider below infinite sums with~$\oplus$.
A semiring~$\Semiring$ is called \emph{complete} 
if for every family
$(x_i)_{i \in I}$ %$\{ x_i \mid i \in I \}$
of elements of $\dom(\Semiring)$ over an index set $I \subset \mathbb{N}$,
the infinite sum $\bigoplus_{i \in I} x_i$
is well-defined and in $\dom(\Semiring)$,
and the following properties hold:
\begin{description}
\item[$i.$]
\emph{infinite sums extend finite sums:}
$\displaystyle\bigoplus_{i \in \emptyset} x_i = \zero$,\quad 
      $\forall j\in \mathbb{N}, \displaystyle\bigoplus_{i \in \{ j \}} x_i = x_j$,\quad
      $\forall j, k\in \mathbb{N}, j\neq k, 
      \displaystyle\bigoplus_{i \in \{ j, k \}} x_i = x_j \oplus x_k$,
%
\item[$ii.$]
\emph{associativity and commutativity:}
for all $I \subseteq \mathbb{N}$
and all partition $(I_{j})_{j \in J}$ of $I$, %\subseteq \mathbb{N}$, 
\(
\displaystyle
\bigoplus_{j \in J}\bigoplus_{i \in I_j} x_i = 
\bigoplus_{i \in I} x_i
\),
%
\item[$iii.$] 
\emph{distributivity of product over infinite sum:}\\
for all $I \subseteq \mathbb{N}$,
\(
\displaystyle
\bigoplus_{i \in I} (x \otimes y_i) = x \otimes \bigoplus_{i\in I} y_i\), and
\(
\displaystyle
\bigoplus_{i \in I} (x_i \otimes y) = (\bigoplus_{i \in I} x_i ) \otimes y\).
\end{description}

\subsection{Label Theory}
\label{section:symbols}

Let $\Sigma$ and $\Delta$ be respectively an input and output \emph{alphabets}, 
which are countable (finite or infinite) sets of symbols, 
and let $\Semiring$ be a commutative semiring.

\noindent 
A \emph{label theory} is made of 4 recursively enumerable sets:
%$\Phi_0$, \Phi_\Sigma \uplus \Phi_\Delta \uplus \Phi_{\Sigma, \Delta}$ 
$\Phi_\epsilon \subseteq \Semiring$, % containing constant functions valued in $\Semiring$, 
$\Phi_\Sigma$ and $\Phi_\Delta$, 
containing unary functions in $\Sigma \to \Semiring$, resp. $\Delta \to \Semiring$, 
and $\Phi_{\Sigma, \Delta}$  containing binary functions in $\Sigma \times \Delta \to \Semiring$.
Moreover, we assume that these sets are closed under the operators 
$\oplus$ and $\otimes$ of~$\Semiring$.
More precisely, for all $\phi, \phi' \in \Phi_\Sigma$ all 
$\psi, \psi' \in \Phi_\Delta$, 
and $\eta, \eta' \in \Phi_{\Sigma, \Delta}$, the function
\begin{description}
\item $\phi \otimes \phi' : x \mapsto \phi(x) \otimes \phi'(x)$ belongs to $\Phi_\Sigma$, 
\item $\psi \otimes \psi' : y \mapsto \psi(y) \otimes \psi'(y)$ belongs to $\Phi_\Delta$,
\item $\phi \otimes \eta : x, y \mapsto \phi(x) \otimes \eta(x, y)$ belongs to $\Phi_{\Sigma, \Delta}$,
\item $\eta \otimes \psi : x, y \mapsto \eta(x, y) \otimes \psi(y)$ belongs to $\Phi_{\Sigma, \Delta}$,
\item $\eta \otimes \eta' : x, y \mapsto \eta(x, y) \otimes \eta'(x, y)$ belongs to $\Phi_{\Sigma, \Delta}$.
\end{description}
The same also holds for the binary sum operator $\oplus$.

\noindent
\marginpar{maybe not necessary}
Finally, it is assumed that the codomain of every function of $\Phi_\Sigma$ and $\Phi_\Delta$
is a subset of $\Phi_\epsilon$.
and all partial applications of functions $\Phi_{\Sigma, \Delta}$, 
resp.  $f_a: y \mapsto f(a, y)$ for $a \in \Sigma$ and $y \in \Delta$
and  $f_b: x \mapsto f(x, b)$ for $b \in \Delta$ and $x \in \Sigma$, 
belong resp. to $\Phi_\Sigma$ and $\Phi_\Delta$.

@@

Let $\Sigma$ be a countable alphabet 
%finite (large) or infinite,
that we assume partitioned into :
\begin{itemize}
\item a set $\Sigmai$ of \emph{internal symbols} denoted $a$,
\item a set $\Sigmac$ of \emph{call symbols} denoted $\call{a}$,
\item a set $\Sigmar$ of \emph{return symbols} denoted $\return{a}$.
\end{itemize}
Let $\Semiring$ be a commutative semiring and  
let  $(\Phi_\epsilon, \Phic, \Phir, \Phicr)$ be a label theory over $\Semiring$
%In order to simplify notations, %and following the definition of Section~\ref{section:transducer}, 
%we shall write respectively 
where $\Phic$, $\Phir$ and~$\Phicr$ stand respectively 
for~$\Phi_\Sigmac$, $\Phi_\Sigmar$ and~$\Phi_{\Sigmac, \Sigmar}$.
%
Moreover, we extend this theory with a set $\Phii$ 
of unary functions in $\Sigmai \to \Semiring$,
closed under $\oplus$ and $\otimes$.

\begin{definition}
A \emph{Symbolic Weighted Visibly Pushdown Automata} (\SWVPA)~$A$ 
over  $\Sigma = \Sigmai \uplus \Sigmac \uplus \Sigmar$ and $\Semiring$ is a tuple
$T = \< Q, P, \init, \weii, \weic, \weir, \weie, \final >$,
where $Q$ is a finite set of states, 
$P$ is a finite set of stack symbols, 
$\mathsf{in} : Q \to \Semiring$, 
respectively $\mathsf{out} : Q \to \Semiring,$
are functions defining the weight for entering, 
respectively leaving, a state, 
and 
$\weii : Q \times Q \to \Phii$,  
$\weic : Q \times Q \times P \to \Phic$,  
$\weir : Q \times P \times Q \to \Phicr$,  
$\weie : Q \times Q \to \Phir$,  
are transition functions.
\end{definition}
%
Similarly as in Section~\ref{section:transducer}, 
we extend the above transition functions as follows
for all $q, q' \in Q$, $p \in P$, 
$a \in \Sigmai$, 
$\call{c} \in \Sigmac$, 
$\return{r} \in \Sigmar$, 
overloading the names for simplicity:
\[
\begin{array}{lll}
\weii: Q \times \Sigmai \times Q \to \Semiring & 
\weii(q, a, q') = \phi_\mathsf{i}(a) & 
\mathrm{where~} \phi_\mathsf{i} = \weii(q, q'),\\
%
\weic: Q \times \Sigmac \times Q \times P \to \Semiring & 
\weic(q, \call{c}, q', p) = \phi_\mathsf{c}(\call{c}) & 
\mathrm{where~} \phi_\mathsf{c} = \weic(q, q', p),\\
%
\weir: Q \times \Sigmac \times P \times \Sigmar \times Q \to \Semiring & 
\weir(q, {\call{c}},  p, {\return{r}}, q') = \phi_\mathsf{r}({\call{c}},  {\return{r}}) & 
\mathrm{where~} \phi_\mathsf{r} = \weir(q, p, q'),\\
%
\weie: Q \times \Sigmar \times Q \to \Semiring & 
\weie(q, {\return{r}}, q') = \phi_\mathsf{e}({\return{r}}) &
\mathrm{where~} \phi_\mathsf{e} = \weie(q, q').\\
\end{array}      
\]

\noindent
The intuition is the following for the above transitions.
\begin{description}
\item $\weii$ : read the input internal symbol $a$, change state to $q'$.
\item $\weic$ : read the input call symbol $\call{c}$, push it to the stack along with $p$, change state to $q'$.
\item $\weir$ : when the stack is not empty, 
      read and pop from stack a pair made of $\call{c}$ and $p$, 
      read the input return symbol $\return{r}$, change state to $q'$.
      In this case, the weight function $\phi_\mathsf{r}$ 
      computes the value of matching between the call and return symbols.
      It might be $\zero$ to express that the symbols do not match.
\item $\weie$ : when the stack is empty, 
      read the input symbol $\call{r}$, change state to $q'$.
\end{description}

@@

\noindent
The weight associated by $A$ to $s \in \Sigma^*$
is then defined as follows,
following empty stack semantics: 
\[
A(s)  = 
{\displaystyle\bigoplus_{q, q' \in Q}} \textstyle
\mathsf{in}(q) \mathop{\otimes} 
\weight_A\bigl(\config{q}{\bot}, s, \config{q'}{\bot}\bigr) 
\mathop{\otimes} \mathsf{out}(q').
\]

\subsection{1-best Computation}

Regarding the infinite sum operator, it must hold that
$\bigoplus_{x \in \Phi_\Sigma} \phi(x)$, 
$\bigoplus_{y \in \Phi_\Delta} \psi(y)$, and

@@

property of bounded convexity of weight functions:
